Automating Verification of MPC Security

### 2023-06-05 popl24/minicat.tex
checkpoint

We model probabilistic programming via the \emph{random tape}
approach. That is, we will assume that programs can make reference to
values chosen from a uniform random distribution- coin ``flips''- via
values arbitrarily assigned in the initial program memory- the random
tape. Programs execute deterministically given the random tape.

>>>>

We model probabilistic programming via the \emph{random tape}
approach. That is, we will assume that programs can make reference to
values chosen from a uniform random distribution- coin ``flips''- via
values arbitrarily assigned in the initial program memory.  Programs
execute deterministically given the random tape. The random tape
formulation supports our automated analysis as we discuss in
section
